---
title: "Fall2023_Quiz1"
output: html_document
date: "`r Sys.Date()`"
author: ""
date: ""
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r load-packages, message = FALSE}
library(tidyverse)
```

# Data

```{r load-data, message = FALSE}
drugs <- read_csv("data/drugs.csv")
```

# Task 1.1

```{r}


```

# Task 1.2

```{r}


```

How many such cases are there in the dataset where the age is less than 30? What is the percentage of those cases to the total cases in the dataset?

# Task 1.3

```{r}



```


# Task 2.1

```{r}



```

# Task 3.1

```{r}



```
Which race category shows the highest median age based on the box plot?


# Task 3.2

```{r}



```
What can you infer about the age distribution based on the histograms?


# Task 3.3

```{r}



```
Based on the faceted histogram, what insights can you draw regarding the age distribution differences among races and genders in drug-related deaths?


# Task 4.1

```{r}



```

# Task 5.1

```{r}



```

